Constructing the transition graphs of interacting hysterons

### 2022-06-28 Paper_draft.tex
Added piece about ordering of switching fields

>>>>

\subsection{Evaluation of switching fields}
We now describe how the transition graph is constructed for a given set of bare switching fields $\{u_i^{+, -}\}$ and coupling coefficients $c_{ij}$.\\
We observe that in essence, it is only the ordering of the switching fields ${U_i^{+, -}(S)}$ that determines the state transition graph, rather than their absolute value. As a result, there can only be as many graphs as there are permutations of the order of switching fields. In the case where hysterons are non-interacting, there are only $2N$ switching fields $\{u_i^{+, -}\}$. In addition, because we never compare an up switching field with a down switching fields, the only orderings that can change the graph are the partial orderings of the up switching fields $\{u_i^+\}$ and of the down switching fields $\{u_i^-\}$. The number of orderings that can lead to a unique graph is then $N!\times N!$. When we fix the up switching fields to account for exchange symmetry, we find that the number of permutations is only $N!$. Indeed, we have that there are $N!$ Preisach graphs for a collection of $N$ hysterons, each corresponding to a different main loop.\\ 
When hysterons are allowed to interact, however, the situation changes. On one hand, there are then $2(2^N-1)$ states $U_i^{+, -}(S)$, and because of the possibility of avalanches, the ordering between all of the states must be considered. On the other hand, the state transition graph is only determined by a partial order between some of the switching fields. As a result, the number of permutations greatly outnumbers the number of unique state transition graphs. For $N=2$, the number of permutations is $8! = 40320$ while we know the number of graphs to be 13. For $N=3$, the number of permutations is as high as $24! \approx 6\times 10^{23}$.\\
We conclude that it is inefficient to find all graphs for an interacting system of hysterons by considering the permutations of all switching fields. Even so, we can make use of the fact that the state transition graph only depends on a partial ordering of the switching fields. Namely, we know that each graph has an underlying set of linear inequalities $U_i(S_A) > U_j(S_B)$, which we refer to as the design inequalities\cite{vhecke2021}. The solution space of the design inequalities provides the region in parameter space that leads to the given graph. In particular, if the design inequalities have no solution, then the given graph is not realizable.\\
